---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```
# Self Assessment: Session 1

## Instructions

**Welcome!**

*This app is still very nascent, please alert me of any errors or unexpected behaviour.*

If this is your first time in DB Browser for SQLite, the following instructions may help:

#### 1) Load Database
- Open DB Browser for SQLite
- Go to File > Open Database
- Navigate to your chinook.db 
	- This will be wherever you cloned the GH Repo (within the **SQL** folder)
	- ![8338a7f3d843398c3b7b395eae3e1994.png](:/9bf5034c5dbf4aa6a9f243fc26800c01)

#### 2) Configure your windows
By default, DB Browser for SQLite has three windows, with four tabs in the main window and three tabs in the bottom right window
- Window 1: Main Window (Centre)
	- Stay in the Database Structure tab for now
- Window 2: Edit Database Cell (Top Right)
- Window 3: Remote (Bottom Right)
	- Switch this to DB Schema tab (very bottom)

Your screen should look like this (or very similar)
![4159f1cda9ef0b41aa174e161164edb8.png](:/5b830208e10f4060828db394a566f1c0)

#### 3) The chinook.db
There are 11 tables in the Main Window:

1. Album
2. Artist
3. Customer
4. Employee
5. Genre
6. Invoice
7. InvoiceLine
8. MediaType
9. Playlist
10. PlaylistTrack
11. Track

Switch to the Browse Data tab, Album is selected by default
 <img src=":/2be5c3dfb42345fa85c53fd87ee74cd0" width="900"> 


Using the table drop down at the top left, explore some of the contents of the database
 <img src=":/bf58ac331e944dacb07b0be159c41638" width="200"> 
 
**Click Next Topic when you're ready to begin**

## Commenting Out SQL Code

```{r code-comment, echo=FALSE}
question("How do you comment code out in SQL?",
  answer("`# SELECT...`"),
  answer("`-- SELECT...`", correct = TRUE),
  answer("`/* SELECT... */`", correct = TRUE),
  answer("`// SELECT...`"),
  random_answer_order = TRUE,
  allow_retry = TRUE
)
```

## Data Types

```{r data-type, echo=FALSE}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```


## Relationships

```{r relationships, echo=FALSE}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

## Primary Keys

```{r pks, echo=FALSE}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```



